Modelling circumstellar discs with 3D radiation hydrodynamics

### 2009-09-28 SPH-Torus-paper1/sphtorus_benchmark.tex
Added a paragraph on timing and RT overhead.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2033 25464f21-6099-402c-b30a-640f1d40d38b

>>>>

Monte-Carlo radiative transfer calculations can be computationally
demanding so the calculation was parallelised using MPI (Message
Passing Interface) libraries. Parallelising code in this way allows
for parallel computation in both the radiation and hydrodynamics steps
and can be applied to a shared memory or a distributed memory computer
architecture. Evolving the disc using both the radiation and
hydrodynamics codes took a total wall time of 560 hours using 128 MPI
processes, of which 440 hours was spent in radiation calculations. The
radiation calculations take approximately 4~times as long as the
hydrodynamics calculations so the combined code is significantly
slower than the SPH code alone. However the calculation is still
feasible and we expect the combined code to be used in applications
where the increased accuracy of the Monte-Carlo radiation calculation,
over faster alternatives, is of importance.
